A 3d curvilinear skeletonization algorithm with application to path tracing

### 2012-09-14 application_to_path_tracing.tex
on va voir

$L$ is the radiance (a radiometric quantity that represents luminosity) from point $x$ toward direction $\Theta$. $L_e$ is the emitted radiance (non null only on light sources). The point $r(x, \Phi)$ is the nearest visible point from $x$ in the direction $\Phi$ of the hemisphere $\Omega_x$. The $f_s$ function expresses how much luminosity is exchanged, on point $x$, between an incoming ray $\Phi$ and the outgoing ray $\Theta$. Intuitively it represents the material properties of the surface at point $x$.

@@

The algorithm computes $L$ as follow: first, it chooses one random direction $\Phi$ based on the pdf $p$. Then, it applies the estimator by calling $L$ recursively to compute $L_r$ (shoots a new ray in the direction $\Phi$, computes the new hit point with the scene, and compute the new radiance at this point). Finally, it returns the sum of the emitted radiance $L_e$ and the result for $L_r$. The recursion stops when a maximal number of bounces has been reached.
%ASK: euh, c'est L ou L_r%
%c'est bon de dire que ça s'arrete au light%

This computation is done multiple times for each pixel (at different positions over the pixel). We average the results and get an estimation of the mean radiance passing through the pixel and heading towards the camera.
%at different positions over the pixel  ???%
A bad pdf would lead in picking directions that don't reach the light before the end of the recursion, and produce results with a lot of noise in the final image. In the next part, we explain how to produce a pdf based on the curvilinear skeleton.

@@

%a revoir, je ne comprends pas tout

@@

It is a product of two functions that can be efficiently sampled individually but that are hard to sample when they are combined. The most common strategy used to sample $\Omega_x$ is to use the function $f_s$ because we know it: it is given as an input of the algorithm, for exemple with textures that describe materials.

The term $L$ is rarely used because its evaluation cannot be done in constant time. Remember that it represents the distribution of light in the scene. It takes high values when $\Phi$ carries a lot of energy. Our method gives a way to sample according to $L$.

@@

The skeleton of the voids of the scene is computed using Alg.~\ref{algo::3d_curvskel} and is converted to a graph (the nodes are the 0-faces and the edges are the 1-faces). We then compute a set of \myem{importance points}: these points will be used to sample $\Omega_x$ in the path tracing algorithm. For each node of the skeleton $n$, one importance point $imp_n$ is computed. Intuitively, the importance point associated to $n$ gives us a direction to follow in order to find a light source.
%TODO a verifier quand meme

%La, pas clair !!!
Let $L$ be a light source of the scene ($L \in S_L$) and $n_L$ the nearest node that is visible by $L$. We first compute a tree of shortest paths along the skeleton with $n_L$ as root. We use the Dijkstra algorithm with a distance based on visibility from $n_L$: We put $d(n, m) = 1$ if $m$ is visible from $n_L$ and $d(n, m) = 10$ if not. It results that the paths that are enlighted by $L$ will have a shorter distance and will guide us to the light faster than the dark ones.

Let $n$ be a node of the skeleton and $V_n$ the set of visible nodes from $n$ along the shortest path toward $n_L$. The importance point $imp_n$ associated to $n$ is the barycenter of $V_n$.

\begin{center}
\includegraphics[scale=0.5]{images/importance_points.png}
\end{center}

@@

Given a point $x$ and a direction $\Theta$ we want to compute $L(x \rightarrow \Theta)$ and then sample the hemisphere $\Omega_x$. We search for the nearest skeleton node $n$ and its importance point $imp_n$. We sample the hemisphere with a power-cosine pdf centered on $\overrightarrow{ximp_n}$:
\begin{equation*}
p_{skel}(\Phi) = \frac{s + 1}{2\pi} cos^s \alpha
\end{equation*}
with $\alpha$ the angle between $\overrightarrow{ximp_n}$ and $\Phi$, $s$ being a parameter called skeleton strength. The higher $s$ is, the more we sample close $\overrightarrow{ximp_n}$.

@@

Some results are presented in figure~\ref{fig:results} where we can see the decrease in noise compare to the regular path tracing. We computed the MSE value for different scenes that are presented in table~\ref{tab:timing}

@@

\begin{table}[t!]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Scene & fig.\ref{fig:redcorridor} & fig.\ref{fig:examples} far left & fig.\ref{fig:examples} far right \\
\hline
MSE 100& 145 / 57 & 301 / 156 & 881 / 826 \\
\hline
MSE 40& 434 / 260 & 924 / 628 & 2678 / 2570 \\
\hline
\end{tabular}
\caption{Timing(s) to reach an MSE of 100 and 40 against reference images. In each cell, the left number is for the standard path tracing, the right one  our method}
\label{tab:timing}
\end{table}

>>>>

$L$ is the radiance (a radiometric quantity that represents luminosity) from point $x$ toward direction $\Theta$. $L_e$ is the emitted radiance (non null only on light sources). The point $r(x, \Phi)$ is the nearest visible point from $x$ in the direction $\Phi$ of the hemisphere $\Omega_x$. The $f_s$ function expresses how much luminosity is exchanged, on point $x$, between an incoming ray $\Phi$ and the outgoing ray $\Theta$. It represents the material properties of the surface at point $x$.

@@

The algorithm computes $L$ as follow: first, it chooses one random direction $\Phi$ based on the pdf $p$. Then, it applies the estimator by calling $L$ recursively to compute $L_r$ (shoots a new ray in the direction $\Phi$, computes the new hit point with the scene, and compute the new radiance at this point). Finally, it returns the sum of the emitted radiance $L_e$ and the result for $L_r$. The recursion stops when a maximal number of bounces has been reached.

This computation is done multiple times for each pixel (at different positions over the pixel). We average the results and get an estimation of the mean radiance passing through the pixel and heading towards the camera.
A bad pdf would lead in picking directions that don't reach the light before the end of the recursion, and produce results with a lot of noise in the final image. In the next part, we explain how to produce a pdf based on the curvilinear skeleton.

@@

@@

The most common strategy used to sample $\Omega_x$ is to use the function $f_s$ because it is an input of the algorithm.
The term $L$, which represents the distribution of light in the scene, is unknown. Our method gives a way to sample according to $L$.

@@

The skeleton of the voids of the scene is computed using Alg.~\ref{algo::3d_curvskel} and is converted to a graph (the nodes are the 0-faces and the edges are the 1-faces). We then compute a set of \myem{importance points}, which will be used to sample $\Omega_x$ in the path tracing algorithm. To each node $n$ of the skeleton, one importance point $imp_n$ is computed. Intuitively, the importance point associated to $n$ is the direction to follow in order to find a light source.

%La, pas clair !!!
Let $L$ be a light source of the scene and $n_L$ the nearest node of the skeleton that is visible by $L$. For each node, we compute the shortest path to $n_L$ along the skeleton. To do so, we use the Dijkstra algorithm and weight the edges of the skeleton depending on a visibility criteria: the weight of an edge $e$ is $1$ if $e$ is visible from $n_L$ and $10$ else. It results that the paths that are illuminated by a light will be shorter than paths located in dark areas.

Let $n$ be a node of the skeleton and $V_n$ the set of visible nodes from $n$ along the shortest path toward $n_L$. The importance point $imp_n$ associated to $n$ is the barycenter of $V_n$. An example is shown on Fig.~\ref{fig::example_imp}.

\begin{figure}[tb]
\begin{center}
\begin{tabular}{c|c}
	\myincludegraphics{0.3\textwidth}{graph_heuristic.pdf} &
	\myincludegraphics{0.3\textwidth}{graph_heuristic.pdf} \\
\end{tabular}
\caption[Example of importance point construction]{\label{fig::example_imp} \textbf{On the left}, we illustrate the importance point $imp_n$ associated to a node $n$. The dotted black line shows the closest node to $n$ not included in $V_n$. \textbf{On the right}, an example of the curvilinear skeleton (in red) obtained in the Sponza scene.}
\end{center}
\end{figure}

@@

Given a point $x$ on the scene and a direction $\Theta$, we want to compute $L(x \rightarrow \Theta)$ and then sample the hemisphere $\Omega_x$. We search for the nearest skeleton node $n$ to $x$ and its importance point $imp_n$. We sample the hemisphere with a power-cosine pdf centered on $\overrightarrow{x\,imp_n}$:
\begin{equation*}
p_{skel}(\Phi) = \frac{s + 1}{2\pi} cos^s \alpha
\end{equation*}
with $\alpha$ the angle between $\overrightarrow{x\,imp_n}$ and $\Phi$, $s$ being a parameter called skeleton strength. The higher $s$ is, the closer to $\overrightarrow{x\,imp_n}$ we sample.

@@

Some results are presented on Fig.~\ref{fig:results} and Fig.~\ref{fig::intro_image} where we can see that our method produce less noisy images compared to the regular path tracing. We present, in table~\ref{tab:timing}, the time taken by each method to produce an image of same quality (the quality is measured by the mean square error (MSE) with a reference image) in different scenes.

@@

\begin{figure}[tb]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Scene & fig.\ref{fig:redcorridor} & fig.\ref{fig:examples} far left & fig.\ref{fig:examples} far right \\
\hline
MSE 100& 145 / 57 & 301 / 156 & 881 / 826 \\
\hline
MSE 40& 434 / 260 & 924 / 628 & 2678 / 2570 \\
\hline
\end{tabular}
\caption{Time to reach an MSE of 100 and 40 against reference images. In each cell, the left number is for the standard path tracing, the right is for our method}
\label{tab:timing}
\end{figure}

### 2012-09-14 skeleton_and_pathtracing.tex
on va voir

\begin{abstract}
We present a novel 3d curvilinear skeletonization algorithm which produces filtered skeletons without needing any user input, thanks to a new parallel algorithm based on the cubical complex framework. We then propose a new path tracing algorithm which uses such curvilinear skeleton in order to produce less noisy images in less time than the classical approach.
\end{abstract}

@@

Path tracing algorithms are able to render photorealistic images from a scene description by simulating light propagation. The photorealistic aspect is achieved by simulating diffusion of light: elements of the scene which are illuminated by a light source can cast part of the light they receive. Consequently, parts of the scene which are not directly illuminated by any light source actually receive light, thus giving a realistic effect of light diffusion to the resulting image.

A path tracing algorithm sends rays (of light) from the camera (the viewpoint of the scene), and let them bounce around the scene until they encounter a directly illuminated zone. When a ray hits a point of an object (like a wall), it gathers information on the object's material. The ray is then reemitted in a random direction. Once a ray reaches a light source, the information it gathered through its journey in the scene is averaged in order to decide of the color of the first impact point. This color is then allocated to one of the pixels of the image, and the process is repeated for each pixel of the output image. To avoid \quotes{unrealistic} results due to an unusual reemission direction of a ray, the algorithm actually sends, for each pixel of the image, many rays: the more rays, the longer the algorithm will take to produce an image, but the more realistic the result will look. A path tracing can be seen as a random walk process through the scene.

In order to avoid infinite bouncing of rays in the scene, a limit is set for the number of bounces a ray can do. If a ray does not reach any light source after a given number of bounces, it is eliminated from the scene. A lost ray is as a waste of computation time, and minimizing this loss would speed up the algorithm.

Our proposition is to reduce both the time taken by a path tracing algorithms and the noise in the output images by guiding rays towards the scene's light sources, thus reducing the number of rays \quotes{lost} during the computation. To do this, we perform some precomputation on the void space of the scene (the medium where the rays of light propagate) in order to have, later in the algorithm, a clue on towards which direction a ray should bounce in order to meet a light source. Such precomputation can take time and become more expensive than the original algorithm.

@@

\begin{figure}[tb]
\begin{center}
\begin{tabular}{cc}
	\myincludegraphics{0.60\textwidth}{dgci_ray_corridor.png} &
	\myincludegraphics{0.40\textwidth}{dgci_compare_door.png}
\end{tabular}
\caption{Images $a$ and $b$ shows some rays of the path tracing guided by the material of the objects (image $a$) or our skeleton based method (image $b$). Images $c$ and $d$ point out the noise reduction between the classic path tracing (image $c$) and our method (image $d$)}
\end{center}
\end{figure}

The purpose of this paper is twofold: we first introduce a new curvilinear skeletonization algorithm (Sec.~\ref{sec::skeletonization}) in the cubical complex framework (Sec.~\ref{sec::binary_to_cubic}), producing filtered skeletons without needing any user input (Sec.~\ref{sec::aspect_no_param}). 
Then, we expose a new method, based on such skeletons, to enhance the results and the performance of a path tracing algorithm (see Sec.~\ref{sec::appli_pathtrace}).

>>>>

\begin{abstract}
We present a novel 3d curvilinear skeletonization algorithm which produces filtered skeletons without needing any user input, thanks to a new parallel algorithm based on the cubical complex framework. These skeletons are used a new path tracing algorithm in order to produce less noisy images in less time than the classical approach.
\end{abstract}

@@

Path tracing algorithms~\cite{Ka86,LW93} are able to render photorealistic images from a scene description by simulating light propagation. The photorealistic aspect is achieved by simulating diffusion of light: elements of the scene which are illuminated by a light source can cast part of the light they receive. Consequently, parts of the scene which are not directly illuminated by any light source actually receive light, thus giving a realistic effect of light diffusion to the resulting image.

A path tracing algorithm sends rays from the camera, and let them bounce around the scene until they encounter a directly illuminated zone. When a ray hits a point of any surface, it is reemitted in a random direction. Once a ray reaches a directly illuminated area, all luminance gathered through its journey in the scene is averaged in order to set the color one of the pixels of the image, and the process is repeated for each pixel of the output image. To avoid the noise resulting from this stochastic process, the algorithm actually sends, for each pixel of the image, many rays: the more rays, the longer the algorithm will take to produce an image, but the more realistic the result will look. A path tracing can be seen as a random walk process through the scene.

In order to avoid infinite bouncing of rays in the scene, a limit is set for the number of bounces a ray can do. If a ray does not reach any directly illuminated area after a given number of bounces, its contribution is null. Such lost ray is as a waste of computation time, and minimizing this loss would speed up the algorithm.

Our proposition is to reduce both the time taken by a path tracing algorithms and the noise in the output images by guiding rays towards the scene's light sources, thus reducing the number of rays \quotes{lost} during the computation. To do this, we perform some precomputation on the void space of the scene (the medium where the rays of light propagate) in order to have, later in the algorithm, a clue on towards which direction a ray should bounce in order to meet a light source. Unfortunately, such precomputation may take time and become more expensive than the original algorithm.

@@

\begin{figure}[tb]
\begin{center}
\begin{tabular}{cc}
	\myincludegraphics{0.60\textwidth}{dgci_ray_corridor.png} &
	\myincludegraphics{0.40\textwidth}{dgci_compare_door.png}
\end{tabular}

\caption{\label{fig::intro_image} Images $a$ and $b$ shows some rays of the path tracing guided by the material of the objects (image $a$) or our skeleton based method (image $b$). Images $c$ and $d$ point out the noise reduction between the classic path tracing (image $c$) and our method (image $d$).}
\end{center}
\end{figure}

The purpose of this paper is twofold: we first introduce a new curvilinear skeletonization algorithm (Sec.~\ref{sec::skeletonization}) in the cubical complex framework (Sec.~\ref{sec::binary_to_cubic}), producing filtered skeletons without needing any user input (Sec.~\ref{sec::aspect_no_param}). 
Then, we expose a new method, based on such skeletons, to enhance the results and the performance of the path tracing algorithm (see Sec.~\ref{sec::appli_pathtrace}).
